---
title: "Stimuli for Speech-in-noise-online (SINON) experiment" 
abstract: "In the SINON project we present German words and pseudowords in different types of noise and at different levels. Subjects will perform different tasks: a lexical decision, a 4FC and a picture matching task. We built stimuli using items from MULTIPIC database (picture task) and their corresponding entries in SUBTLEX (word frequency info) and CLEARPOND (phonological info) databases. Then we used WUGGY to create matching pseudowords (non word generator).[...]" 
runhead: "SINON-Stimuli-Deutsch"
author:
  name: Gorka Fraga Gonzalez, Isabelle Goy, Samuel Mueller
  affiliation: University of Zurich 
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
      code_folding: hide
      highlight: espresso
      theme: spacelab
      toc: true
      toc_float:
          collapsed: false
          smooth_scroll: true
          toc_depth: 6

---

# Data available: summary


```{r }
fileinput  <-   "C:/Users/gfraga/Downloads/Neuroling_SINON_stimuli.xlsx"
dat <- openxlsx::read.xlsx(fileinput, sheet = 'Multipic-DE')

  dat <- dat %>% dplyr::mutate_if(is.numeric, round, digits=2)
  reactable(dat,filterable = TRUE, 
            #defaultColDef = colDef( align = "center"),
            height=800,outlined=TRUE,
            minRows= 10, sortable = TRUE,
              theme = reactableTheme(tableBodyStyle = list(flex = "auto"))
)

```





```





```{r, include=FALSE}
    #rmarkdown::render("SINEEG_pilot.Rmd",output_dir = 'W:/Gorka_share',output_file = 'SIN-EEG_pilot', output_format = c("html_document"))
    dirinput<-   "C:/Users/gfraga/scripts_neulin/SINON_experiment"
    knitr::opts_knit$set(root.dir = dirinput)    
    knitr::opts_chunk$set(echo=TRUE,warning=FALSE)
    library(plotly)
    library(tidyr)
    library(dplyr)
    library(reactable)
  #  source('W:/share_gfraga/scripts_neulin/SINEEG/funs/eeg_funs.R')
    

    
```

some more text 

```{r, include = FALSE}
options(width=60)
local({
  hook_output <- knitr::knit_hooks$get('output')
  knitr::knit_hooks$set(output = function(x,options) {
    if (!is.null(options$max.height)) options$attr.output <- c(
      options$attr.output,
      sprintf('style="max-height: %s;"',options$max.height)
    )
   hook_output(x, options)    
  })
})

```

 
## overview {.tabset .tabset-fade .tabset-pills}

### Plots {.tabset .tabset-fade .tabset-pills}

#### Word orthography

A graph code here to be shown

# ```{r, echo=FALSE}
#  library(DT)
#  dirinput <-   "C:/Users/gfraga/scripts_neulin/SINON_experiment"
#   setwd(dirinput)
#   dat <- openxlsx::read.xlsx("Neuroling_SINON_stimuli.xlsx", sheet = 'Merged_databases_cleaned-DE')
#   dat <- dat %>% dplyr::mutate_if(is.numeric, round, digits=2)
#   
#   d2use <- select(dat,c('SUBTLEX','CORRECT_SPELL'))
#   datatable(d2use, options = list(
#   columnDefs = list(list(className = "dt-left", targets = 4)))) %>%
#   #("SUBTLEX", 1) %>%
#   formatStyle("SUBTLEX",
#               background = styleColorBar(d2use$SUBTLEX, "steelblue", -90), backgroundPosition = "left")
#   
  #plotly::plot_ly(data=dat, y=~SUBTLEX, type='box')
#plotly::plot_ly(data = dat, color = ~CORRECT_SPELL, x = ~SUBTLEX, y = ~CORRECT_SPELL,type='bar',
#                visible='legendonly')        # add_text(x=~SUBTLEX,y=~CORRECT_SPELL,text=~SUBTLEX,textposition="top")
```

#### Word phonology

A graph code here to be shown

```{r, echo=FALSE}
plot(x = 4, y = 10)
```

#### Pseudoword orthography

A graph code here to be shown

```{r , echo=FALSE}
plot(x = 4, y = 10)
```


---
 
### Table 
 

#### Word phonology

A graph code here to be shown

```{r, echo=FALSE}
plot(x = 4, y = 10)
```

#### Pseudoword orthography

A graph code here to be shown

```{r , echo=FALSE}
plot(x = 4, y = 10)
```


---
 
### Table 
```{r,max.height='300px', results='asis'}


```

### {-}
## {-}
<!-- #### subfolders & files -->
<!-- ```{r, max.height = '300px' } -->
<!--   fs::dir_tree(params$dirinput,recurse=TRUE) -->
<!-- ``` -->

<!-- ### {-} -->

<!-- ### Data overview {.tabset}  -->
<!-- #### files available -->

<!-- ```{r, out.width='1000px'} -->
<!--   # Read all files -->
<!--   files <- gsub(".*\\EEG_SIN/", "", dir(params$dirinput,recursive =TRUE))  # trimmed list of subdirectories and files from main data directory  -->

<!--   # Identify unique measurements -->
<!--   measurements <- unique(sapply(strsplit(files,split='/'),'[[',1)) # first directory should indicate measurement -->
<!--   idxs <- formatC(as.numeric(sapply(strsplit(measurements,split = ' '),'[[',2)),  width = 2, format = "d", flag = "0") -->


<!--   #summary content  -->
<!--   datSummary <- list() -->
<!--   for (m in 1:length(measurements)){ -->

<!--     curfiles <- files[grep(pattern = measurements[m],files)]   -->
<!--     datSummary[[m]] <-  as.data.frame(cbind(paste0('M',idxs[m]), -->
<!--                                             length(curfiles),  -->
<!--                                             length(which(grepl(pattern = "*raw.*.eeg",x = curfiles))), -->
<!--                                             length(which(grepl(pattern = "*processed.*.eeg*",x = curfiles))), -->
<!--                                             ifelse(length(which(grepl(pattern = "*.wav$",x = curfiles)))>0,'yes','no'), -->
<!--                                             ifelse(length(which(grepl(pattern = "Readme*",x = curfiles)))>0,'yes','no'))) -->

<!--        } -->

<!--   datSummary <- data.table::rbindlist(datSummary,fill = TRUE) -->
<!--   colnames(datSummary) <- c('measurement','n_total_files','n_rawfiles','n_procecssedfiles','contains_wav','contains_readme') -->


<!--   # Make Interactive table to display -->
<!--    reactable(datSummary,filterable = TRUE,    -->
<!--                         defaultColDef = colDef( align = "center", minWidth = 70,headerStyle = list(background = "#f7f7f8")),   -->
<!--                         bordered = TRUE, highlight =TRUE) -->
<!-- ``` -->

<!-- #### eeg file overview -->
<!-- ```{r, out.width='1000px'} -->


<!--    # Read all files -->
<!--   files <- gsub(".*\\EEG_SIN/", "", dir(params$dirinput,recursive =TRUE))  # trimmed list of subdirectories and files from main data directory  -->

<!--   # Identify unique measurements -->
<!--   measurements <- unique(sapply(strsplit(files,split='/'),'[[',1)) # first directory should indicate measurement -->
<!--   idxs <- formatC(as.numeric(sapply(strsplit(measurements,split = ' '),'[[',2)),  width = 2, format = "d", flag = "0") -->


<!--   #summary content  -->
<!--   datSummary <- list() -->
<!--   for (m in 1:length(measurements)){ -->

<!--     # search files for current measurement -->
<!--     curfiles <- files[grep(pattern = measurements[m],files)]   -->


<!--       # Apply function to summarize file (only processed file) -->
<!--       if (length(which(grepl(pattern = "*processed.vhdr$",x = curfiles)))==1) { -->

<!--               processedfile <- paste0(params$dirinput,'/',curfiles[grep(curfiles,pattern='*processed.vhdr')])  -->

<!--               #run my function -->
<!--               suppressWarnings(fun_check_eeg(processedfile)) -->
<!--               info <- cbind(dimensions, mrkrsInfo) -->

<!--               rm(processedfile) -->

<!--       } else { print(paste0('No file found for ',measurements[m])) -->
<!--        } -->

<!--       # Add to main summary table             -->
<!--       datSummary[[m]] <- cbind(paste0('M',idxs[m]), # measurement  -->
<!--                                length(which(grepl(pattern = "*processed.*.eeg*",x = curfiles))), #count processed files -->
<!--                                info) -->
<!--       colnames(datSummary[[m]])[1:2] <- c('measurement','n_processed_files') -->

<!--   } -->


<!-- datSummary <- data.table::rbindlist(datSummary,fill = TRUE) -->


<!--   # Make Interactive table to display -->
<!--    reactable(datSummary,filterable = TRUE,    -->
<!--                         defaultColDef = colDef( align = "center", minWidth = 70,headerStyle = list(background = "#f7f7f8")),   -->
<!--                         bordered = TRUE, highlight =TRUE) -->
<!-- ``` -->
